Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-08-14 document/ms.tex
Add prose surrounding the violin plot, some other minor edits.

Full-spectrum fitting was performed for 48 of the 54 available IGRINS spectral orders as described in Section \ref{sec:methods} and Appendix \ref{methods-details}.  The MCMC samples had 5000 steps with 40 walkers.  The stellar parameter ranges were $\logg \in [3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the effective temperature range was $\teffa, \teffb \in [2700, 4500]$.  $H-$band fits had normal distribution priors in place: solar metallicity to $\pm0.05$ dex, $logg=3.8\pm0.1$, and $\vsini=29\pm5$ km/s.  The MCMC chains all appeared to converge after about 1500 steps.

Marginalized distributions were computed for all 14 stellar and nuisance parameters by selecting the final 200 $\times$ 40 walkers = 8000 samples, and point estimates were obtained by computing the median, $5^{th}$ and $95^{th}$ percentiles of the marginal distributions.  The fit quality was first assessed by examining the consistency of the point estimates across the spectral orders.  The distribution of $v_z$ and $\vsini$ were informative for finding extremely poor fits.  The range for all 48 orders was $v_z = 12.4 \pm 2.6$ km/s and $\vsini = 28.8 \pm 2.0$ km/s.  Two orders with poor telluric correction ($o=91$ and $94$) had exceptionally large uncertainties on their values for $v_z$ and $\vsini$.

The posteriors on $\teffa$ and $\teffb$ show several trends- see Figure \ref{fig:TwoTempResults} and Appendix Table \ref{tbl_order_results} for the results of effective temperatures for all IGRINS orders.  \todo{Explain this more.}

Overplotting models with the observed spectra yielded insights on why some orders failed, and which orders can discriminate between starspots and ambient photospheric lines the best.  Some orders are dominated by spectral line outliers--deep metal lines that cannot be described by a coarse metallicity estimate alone.  These spectral line outlier orders also tend to bias estimates of effective temperature.  These metal lines can also be biased by Zeeman broadening, which would explain the heightened effect size with wavelength.

\todo{insert results from re-run of H-band spectra here}
Nearly-equal solutions could be explained by vanishingly weak spectral lines in one or the other of the effective temperature ranges, in which case the method offers little constraint on $\teffb$, but improves the fit around $\teffa$.

>>>>

Full-spectrum fitting was performed for 48 of the 54 available IGRINS spectral orders as described in Section \ref{sec:methods} and Appendix \ref{methods-details}.  The MCMC samples generally had 5000 steps with 40 walkers.  The stellar parameter ranges were $\logg \in [3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the effective temperature range was $\teffa, \teffb \in [2700, 4500]$.  $H-$band fits had normal distribution priors in place: solar metallicity to $\pm0.05$ dex, $logg=3.8\pm0.1$, and $\vsini=29\pm5$ km/s.  The MCMC chains all appeared to converge after about 1500 steps.

Marginalized distributions were computed for all 14 stellar and nuisance parameters by selecting the final 200 $\times$ 40 walkers = 8000 samples, and point estimates were obtained by computing the median, $5^{th}$ and $95^{th}$ percentiles of the marginal distributions.  The fit quality was first assessed by examining the consistency of the point estimates of $v_z$ and $\vsini$ across the spectral orders.  The distribution of $v_z$ and $\vsini$ exposed extremely poor fits in two orders ($o=91$ and $94$), with all other orders demonstrating $v_z = 12.4 \pm 2.6$ km/s and $\vsini = 28.8 \pm 2.0$ km/s.

Overplotting forward-modeled spectra with the observed IGRINS spectra yielded insights on why some spectral orders performed better than others in assessing stellar properties.  This model comparison is performed by sorting the 8000 samples by their fill factor estimates and examining random draws of the cool spectrum, hot spectrum, and composite spectrum, excluding the Gaussian process coveriance and white noise steps.  Fitting defects were conspicuous.  Orders with extremely poor telluric correction residuals, large spectral line outliers, and uncorrected H line residuals from A0V standard division, were all excluded from our final stellar parameter compilation.  Notably, several orders in $K-$band were rejected due to large biases in metallicity, since $K-$band had uninformative priors on $\Z$, resulting in overfitting of orders possessing deep metal lines.  For example, orders $o=$ 79 and 81 overfit Ca~I and Na~I lines and orders $o=74-76$ overfit the CO lines, which are known for their gravity sensitivity \todo{cite}.  These and other metal lines can also be biased by Zeeman broadening, which could explain the heightened effect size with wavelength \todo{cite}.  Additionally, some orders without these conspicuous faults, but simply possessing mediocre fits, or relatively uninformative fits, were also removed from downstream estimates.  What's left were the most informative orders relatively devoid of spectral line outliers.  Figure \ref{fig:TwoTempResults} shows the distribution of $\teffa$ (blue shading), $\teffb$ (red shading), and $\f_{\Omega}$ (yellow shading) for all of the spectral orders, but with the rejected orders grayed out, and the most reliable spectral orders shown in bold.  The point estimates for each spectral order are listed in Appendix Table \ref{tbl_order_results}.
